Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

Define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the input, rather than a tuple.

>>>>

Define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\[-1mm]
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the input, rather than a tuple.
